What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-28 paper/main.tex
kristin's pts 7, 8 - fixed typos

    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time %KYR: FIX!
    is accepted by $G'$. If a path contains an out-edge of $f$, it cannot be in $\L'$ as the trace continues beyond the first time step at $f$. Thus, every trace in $\L'$ only uses edges in $G'$, and is thus accepted by $G$ iff it is accepted by $G'$.
\end{proof}

\begin{theorem}
    For any \Buchi automaton $G$ with start state $s$ and final states $F$, \textbf{ba2wregex}$(G)$ outputs the $\omega$-regular language accepted by $G$.
\end{theorem}
\begin{proof}
    We show that
    \[
        \L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f) \verb|^| \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
    \]
    and the $\omega$-language accepted by $G$, $\L_\omega(G)$ are identical.

    First, $\L\subseteq \L_\omega(G)$ since for every infinite run in $\L$, by definition of $\L$, there is some $f\in F$ such that passes through $f$ infinitely often. The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often; thus the run is in $\textbf{nfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$.
\end{proof}
\subsection{Correctness of Rewrite Rules}
\begin{lemma}
    For all regular expressions $r_1, r_2, r$, each of the following rewrite rules preserve the regular or $\omega$-regular language represented by the expressions:
    \begin{alignat}{2}
        & r_1 + r_1r_2^* && \Longrightarrow r_1r_2^* \\
        & r + r && \Longrightarrow r \\
        & r_1 + r_2^*r_1 && \Longrightarrow r_2^*r_1 \\
        & (r^*)^{\omega} && \Longrightarrow r^{\omega} \\
        & (r_1r_2^*)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & (r_1r_2)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & r^*r^{\omega} && \Longrightarrow r^{\omega} \\
        & rr^{\omega} && \Longrightarrow r^{\omega}
    \end{alignat}
\end{lemma}

>>>>

    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by reaching $f$ for the first time
    is accepted by $G'$. If a path contains an out-edge of $f$, it cannot be in $\L'$ as the trace continues beyond the first time step at $f$. Thus, every trace in $\L'$ only uses edges in $G'$, and is thus accepted by $G$ iff it is accepted by $G'$.
\end{proof}

\begin{theorem}
    For any \Buchi automaton $G$ with start state $s$ and final states $F$, \textbf{ba2wregex}$(G)$ outputs the $\omega$-regular language accepted by $G$.
\end{theorem}
\begin{proof}
    We show that
    \[
        \L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f)  \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
    \]
    and the $\omega$-language accepted by $G$, $\L_\omega(G)$ are identical.

    First, $\L\subseteq \L_\omega(G)$ since for every infinite run in $\L$, by definition of $\L$, there is some $f\in F$ such that passes through $f$ infinitely often. The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often; thus the run is in $\textbf{nfa2regex}(G, s, f)$ $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$.
\end{proof}
\subsection{Correctness of Rewrite Rules}
\begin{lemma}
    For all regular expressions $r_1, r_2, r$, each of the following rewrite rules preserve the regular or $\omega$-regular language represented by the expressions:
    \begin{alignat}{2}
        & r_1 + r_1r_2^* && \Longrightarrow r_1r_2^* \\
        & r + r && \Longrightarrow r \\
        & r_1 + r_2^*r_1 && \Longrightarrow r_2^*r_1 \\
        & (r^*)^{\omega} && \Longrightarrow r^{\omega} \\
        & (r_1r_2^*)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & (r_1r_2)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & r^*r^{\omega} && \Longrightarrow r^{\omega} \\
        & rr^{\omega} && \Longrightarrow r^{\omega}
    \end{alignat}
\end{lemma}
